---
output: github_document
---

[![Travis build status](https://travis-ci.com/muschellij2/mni.svg?branch=master)](https://travis-ci.com/muschellij2/mni)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/muschellij2/mni?branch=master&svg=true)](https://ci.appveyor.com/project/muschellij2/mni)
[![Coverage status](https://codecov.io/gh/muschellij2/mni/branch/master/graph/badge.svg)](https://codecov.io/gh/muschellij2/mni)
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```
# mni Package: 
The goal of `mni` is to provide provides functions for downloading magnetic
    resonace imaging ('MRI') templates of humans.

## Installation

You can install `mni` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("muschellij2/mni")
```


Data from http://nist.mni.mcgill.ca/:

Copyright (C) 1993-2009 Louis Collins, McConnell Brain
Imaging Centre, Montreal Neurological Institute, McGill University.
Permission to use, copy, modify, and distribute this software and
its documentation for any purpose and without fee is hereby granted,
provided that the above copyright notice appear in all copies. The
authors and McGill University make no representations about the
suitability of this software for any purpose. It is provided "as
is" without express or implied warranty. The authors are not
responsible for any data loss, equipment damage, property loss, or
injury to subjects or patients resulting from the use or misuse of
this software package.

Copyright (C) 2016-2018 Yiming Xiao, McConnell Brain Imaging Centre,
Montreal Neurological Institute, McGill University.
Permission to use, copy, modify, and distribute this software and
its documentation for any purpose and without fee is hereby granted,
provided that the above copyright notice appear in all copies. The
authors and McGill University make no representations about the
suitability of this software for any purpose. It is provided "as
is" without express or implied warranty. The authors are not
responsible for any data loss, equipment damage, property loss, or
injury to subjects or patients resulting from the use or misuse of
this software package.

```{r}
citation("mni")
```
